---
title: "Public Opinion and Policy"
subtitle: "POLSCI 4SS3 -- Winter 2024 -- McMaster University"
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
```

## Course Description

This course explores quantitative research designs to answer questions about public opinion and policy in academia, government, and industry. We will examine how to conduct surveys to understand variation in public opinion or attitudes toward several subjects across the world. We will also examine empirical strategies to generate credible evidence to inform policy and decision-making in different contexts.

In this website you will find all the course materials. Assignments must be submitted through [Avenue](https://avenue.mcmaster.ca/).


### Instructor

- {{< fa user >}} &nbsp; [Dr. Gustavo Diaz](https://gustavodiaz.org/)
- {{< fa university >}} &nbsp; KTH 505
- {{< fa envelope >}} &nbsp; <a href="mailto:diazg2@mcmaster.ca">diazg2@mcmaster.ca</a>
- {{< fa calendar-check >}} &nbsp; [Schedule a meeting](https://calendly.com/diazg/student-hours)

### Course details

- {{< fa calendar >}} &nbsp; Thursdays
- {{< fa clock >}} &nbsp; 2:30-5:20 PM
- {{< fa location-dot >}} &nbsp; See [Avenue](https://avenue.mcmaster.ca/)
- {{< fa calendar-alt >}} &nbsp; January 11-April 4, 2024

### Contact

Send an email or schedule a meeting. I usually respond to emails within 24 hours. Please schedule meetings at least 8 hours in advance.

## Schedule


```{r schedule, include = FALSE}
schedule =
  tribble(
    ~Week, ~Date, ~Content, ~Lab,
    1, "January 11", "[Introduction](content/01_content.qmd)", "Getting started",
    2, "January 18", "[The MIDA framework](content/02_content.qmd)", "Intro to R and RStudio",
    3, "January 25", "[Representative surveys](content/03_content.qmd)", "Sampling and descriptive inference",
    4, "February 1", "[Sensitive questions](content/04_content.qmd)", "Reducing sensitivity bias",
    5, "February 8", "[Survey experiments](content/05_content.qmd)", "Survey experimental designs",
    6, "February 15", "[Convenience samples](content/06_content.qmd)", "External validity",
    7, "February 22", "Mid-term recess", NA,
    8, "February 29", "[Evidence-informed policy](content/08_content.qmd)", "Hypothesis testing",
    9, "March 7", "[Field experiments I](content/09_content.qmd)", "Field experimental designs I",
    10, "March 14", "[Field experiments II](content/10_content.qmd)", "Field experimental designs II",
    11, "March 21", "[Beyond experimentation](content/11_content.qmd)", "Writing your own design",
    12, "March 28", "[Quasi-experiments](content/12_content.qmd)", "Quasi-experimental designs",
    13, "April 4", "NO CLASS -- INSTRUCTOR TRAVEL", NA,
    NA, "**April 25**", "**Optional final project due**", NA
  )
```

<div class="centered-table">

```{r show-schedule, echo = FALSE, results = "asis"}
schedule %>% 
  pandoc.table(justify = "rlll",
               col.names = c("{{< fa hashtag >}} Week",
                             "{{< fa calendar >}} Date",
                             "{{< fa book-open-reader >}} Content",
                             "{{< fa laptop-code >}} Lab"),
               split.tables = Inf,
               missing = "")
```

</div>





