---
title: "Week 1: Introduction"
date: "January 11, 2024"
format: html
---

```{r setup, echo = FALSE, results = "asis"}
# Slide showing functions
source(here::here("R", "show_slides.R"))
```

## Overview

We go over the course theme, requirements, and tips to succeed.

The lab assignment for this week is a freebie. You will install R and RStudio and learn a bit about the project oriented workflow. This will be helpful to keep your work on the weekly lab assignments organized.

## Reading

It's the first day. No reading!

## Slides

::: {.callout-tip}
## Navigation

Click on the frame below and use the arrows to navigate. You can type <kbd class="text-info">?</kbd> (or <kbd class="text-info">shift</kbd> + <kbd class="text-info">/</kbd>) to see useful commands.
:::

```{r show-slides, echo = FALSE, results = "asis"}
show_slide("/slides/01_slides")
slide_buttons("/slides/01_slides")
```


## Lab

Getting started [{{< fa file-pdf >}}](labs/01_lab.pdf) [{{< fa brands r-project >}}](https://github.com/gustavo-diaz/popw24/blob/main/docs/content/labs/01_lab.Rmd)

::: {.callout-warning}
## Due

Monday, January 15, 5 PM
:::