---
title: "Week 2: Representative Surveys"
date: "January 18, 2024"
format: html
---

```{r setup, echo = FALSE, results = "asis"}
# Slide showing functions
source(here::here("R", "show_slides.R"))
```

## Overview

Before jumping into public opinion, we start with an overview of the MIDA framework presented in the textbook.

The MIDA framework approaches research design as a series of steps that can be encoded and, therefore, interrogated. This helps us think about how the results of a study may have changed if we had altered elements of its research design.

The lab assignment for this week will be a guided introduction to R.

## Reading

- {{< fa book >}} [RD sections 1-4](https://book.declaredesign.org/introduction/preface.html)


## Slides

::: {.callout-tip}
## Navigation

Click on the frame below and use the arrows to navigate. You can type <kbd class="text-info">?</kbd> (or <kbd class="text-info">shift</kbd> + <kbd class="text-info">/</kbd>) to see useful commands.
:::

```{r show-slides, echo = FALSE, results = "asis"}
show_slide("/slides/02_slides")
slide_buttons("/slides/02_slides")
```


## Lab

Introduction to R and RStudio {{< fa brands r-project >}} (coming soon!)

::: {.callout-warning}
## Due

Monday, January 22, 5 PM
:::