---
title: "Week 3: Representative Surveys"
date: "January 25, 2024"
format: html
---

```{r setup, echo = FALSE, results = "asis"}
# Slide showing functions
source(here::here("R", "show_slides.R"))
```

## Overview

We start the topic of public opinion with representative surveys. The main reason why social scientists conduct surveys is to infer real-world attitudes and behaviors. However, this presents a very difficulty measurement problem. How should questions be asked to produce an accurate measure of the attitude or behavior of interest?

As the name suggests, a representative survey is administered to a sample of respondents that resemble the demographic characteristics of the underlying population.

The punchline of this week is that conducting a true representative survey via random sampling is near impossible. Instead, most surveys use some form of quota or stratified sampling to ensure that the sample obtained resembles the  population of interest.

The lab assignment for this week compares different sampling techniques.

## Reading

- {{< fa book >}} [RD sections 5-7, 15](https://book.declaredesign.org/declaration-diagnosis-redesign/declaring-designs.html) 

- {{< fa file-lines >}} Schwarz, Norbert. 1999. [“Self-reports: How the questions shape the answers.”](https://www.schulich.uwo.ca/familymedicine/research/docs/resources/Self-Reports.pdf) *American Psychologist* 54 (2): 93-105

- {{< fa file-lines >}} Stephenson, Laura B., Allison Harell, Daniel Rubenson, and Peter John Loewen. 2021. [“Measuring Preferences and Behaviors in the 2019 Canadian Election Study.”](https://doi.org/10.1017/S0008423920001006) *Canadian Journal of Political Science/Revue Canadienne de science politique*



## Slides

::: {.callout-tip}
## Navigation

Click on the frame below and use the arrows to navigate. You can type <kbd class="text-info">?</kbd> (or <kbd class="text-info">shift</kbd> + <kbd class="text-info">/</kbd>) to see useful commands.
:::

```{r show-slides, echo = FALSE, results = "asis"}
show_slide("/slides/03_slides")
slide_buttons("/slides/03_slides")
```


## Lab

Sampling and descriptive inference {{< fa brands r-project >}} (coming soon!)

::: {.callout-warning}
## Due

Monday, January 29, 5 PM
:::
