---
title: "Field Experiments I"
date: "March 7, 2023"
format: html
---


```{r setup, echo = FALSE, results = "asis"}
# Slide showing functions
source(here::here("R", "show_slides.R"))
```

## Overview

The next two weeks are about field experiments, also known as randomized controlled trials (RCTs) or A/B testing. These are experiments aimed testing the impact of a policy intervention.

Field experiments are diverse both in terms of design and their domains of application, hence the need for two weeks.

The lab focuses on the stepped-wedge or staggered adoption design.


## Reading

- {{< fa book >}} [RD section 18](https://book.declaredesign.org/library/experimental-causal.html)

- {{< fa file-lines >}} Banerjee, Abhijit, Esther Duflo, and Garima Sharma. 2021. [“Long-Term Effects of the Targeting the Ultra Poor Program.”](https://www.nber.org/system/files/working_papers/w28074/w28074.pdf) *American Economic Review: Insights* 3 (4): 471-486

- {{< fa file-lines >}} Pennycook, Gordon, Ziv Epstein, Mohsen Mosleh, Antonio A. Arechar, Dean Eckles, and David G. Rand. 2021. [“Shifting attention to accuracy can reduce misinformation online.”](https://www.nature.com/articles/s41586-021-03344-2) *Nature* 592: 590-595


## Slides

::: {.callout-tip}
## Navigation

Click on the frame below and use the arrows to navigate. You can type <kbd class="text-info">?</kbd> (or <kbd class="text-info">shift</kbd> + <kbd class="text-info">/</kbd>) to see useful commands.
:::

```{r show-slides, echo = FALSE, results = "asis"}
show_slide("/slides/09_slides")
slide_buttons("/slides/09_slides")
```

## Lab

[Field experimental designs I {{< fa brands r-project >}}](https://github.com/gustavo-diaz/popw24/blob/main/content/labs/09_lab.qmd)

::: {.callout-warning}
## Due

Monday, March 11, 5 PM
:::